Barneby Lives!

### 2023-05-10 scripts/taxonomy_setup.Rmd
subset POWO results lists by whether accepted name is TRUE

```{r}
library(tidyverse)
library(kewr)
```

@@

```{r}
re <- search_powo("Ivesia lycopodioides")

# some considerations....

# If the species cannot be found, RESULTS will be NULL 
search_powo("Ivesia lycopodioides var. lycopodioides")
# if results are NULL, can we strip from subsp./var./ssp. until the end to query only species?

# in the situation where there is a synonym of the group RESULTS will be a list of length two. 
re_syn <- search_powo("Ivesia lycopodioides")
# results will be a list of length 2

# when the appropriate name is searched RESULTS will be a list of length one...
re_perf <- search_powo("Potentilla lycopodioides")

re1 <- re[['results']]

>>>>

```{r}
library(tidyverse)
library(kewr)
library(WorldFlora)
WFO.remember()
source('functions.R')
```

@@

dropped_infra <- search_powo("Ivesia lycopodioides var. lycopodioides")
valid_binomial <- search_powo("Ivesia lycopodioides")
kept_infra <- search_powo("Potentilla lycopodioides var. megalopetala")
what_do_w_authority_autonyms <- search_powo("Potentilla lycopodioides var. lycopodioides")

powo_searcher("Potentilla lycopodioides var. megalopetala")
powo_searcher("Potentilla lycopodioides var. lycopodioides")

lapply(c('Poa annua', 'Linnaea borealis'), powo_searcher)
